Distributed multi-objective evolutionary optimization using island-based selective operator application

### 2019-05-13 hpmoon-asoco.tex
Addresses more comments by reviewer #4

With both chromosome
lengths, increasing the number of islands implies more generations
with all the methods (logically, as there are fewer individuals in each
island). But also, the SLA methods
approach to the number of generations with the baseline when
increasing the number of islands. However, with $L=2048$ the migration
time is big enough  to not improve the number of generations
with respect to the baseline, even in the lower number of islands, as
it happens with $L=512$. Therefore, more generations do not
necessarily mean improve the solution of the global PF, but focusing on
different elements of the chromosome. As  previously stated, every
island is unaware of the other islands PFs, and they are trying to
optimize their solutions independently.

@@

Obtained results also show that when the number of islands
\textcolor{blue}{is increased}, the
automatic overlapping method ($A$) significantly improves the results with
respect to the disjoint and overlapped methods. However, this is only
apparent with larger chromosome sizes. Therefore, the length of the
chromosome is also a key factor to take into account in automatic overlapping
methods, and not only the number of islands. 
%Studying this factor with more types of problems, and new configurations of population size and chromosome lengths could be addressed in the future. 
Since our method divides the individuals into blocks of divisible
size, aggregation methods after migration, such as the ones used in
\cite{Kimovski15Parallel} or \cite{Dorronsoro13superlinear} can be
also tested. But as complete individuals \textcolor{blue}{treated} in
each island, the possibility of using a real number, such as 0.3 (30\%
overlapping) instead an integer value opens future experimental
setups. \textcolor{blue}{This should also take care of epistatic
  interactions between chromosome sizes: although variation operators
  operate on chromosome fragments, selection and fitness evaluation
  operates on the whole chromosome; besides, there is migration
  between islands, so the probability of reaching local minima due to
  this fact is, in fact, going to be avoided.}
For example, comparing 
different ways to calculate $c$ using linear, logarithmic or exponential functions
depending on population size, number of islands, or other values, or using some statistical parameter setting method, such as Taguchi's \cite{Keratmatpour2018Taguchi}.

Although the results obtained in this work are promising, it is clear that this method requires more future experiments, in addition to the automatic calculation of $c$. These new experiments should involve a more complete parameter study, including a sensitivity analysis, to validate our approach. Other benchmarks and real problems should be addressed in the future. These problems could involve dealing with more than two objectives, so polar coordinates should be used to visually understand the results \cite{Li17read}. Also, other MOEA algorithms available in the literature, such as SPEA or MOEA/D could also be compared.

>>>>

With both chromosome
lengths, increasing the number of islands implies more generations
with all the methods (logically, as there are fewer individuals in each
island). But also, the SLA methods
approach to the number of generations with the baseline when
increasing the number of islands. However, with $L=2048$ the migration
time is big enough  to not improve the number of generations
with respect to the baseline, even in the lower number of islands, as
it happens with $L=512$. Therefore, more generations do not
necessarily mean \textcolor{blue}{an improvement in} the solution of the global PF, but focusing on
different elements of the chromosome. As previously stated, every
island is unaware of the other islands PFs, and they are trying to
optimize their solutions independently.

@@

Obtained results also show that when the number of islands
\textcolor{blue}{is increased}, the
automatic overlapping method ($A$) significantly improves the results with
respect to the disjoint and overlapped methods. However, this is only
apparent with larger chromosome sizes. Therefore, the length of the
chromosome is also a key factor to take into account in automatic overlapping
methods, and not only the number of islands. 
%Studying this factor with more types of problems, and new configurations of population size and chromosome lengths could be addressed in the future. 
Since our method divides the individuals into blocks of divisible
size, aggregation methods after migration, such as the ones used in
\cite{Kimovski15Parallel} or \cite{Dorronsoro13superlinear} can be
also tested. But as complete individuals \textcolor{blue}{treated} in
each island, the possibility of using a real number, such as 0.3 (30\%
overlapping) instead an integer value opens future experimental
setups. \textcolor{blue}{This should also take care of epistatic
  interactions between chromosome sizes: although variation operators
  operate on chromosome fragments, selection and fitness evaluation
  operates on the whole chromosome; besides, there is migration
  between islands, so the probability of reaching local minima due to
  this fact is, in fact, going to be avoided.}
For example, comparing 
different ways to calculate $c$ using linear, logarithmic or exponential functions
depending on population size, number of islands, or other values, or
using some statistical parameter setting method, such as Taguchi's
\cite{Keratmatpour2018Taguchi}. \textcolor{blue}{However, taking into
  account that the linear change tested in this paper in fact obtains
  good results with a simple formula, it is our conclusion that
  further complication would not be necessary.}

Although the results obtained in this work are promising, it is clear
that this method requires more future experiments. These new
experiments should involve a more complete parameter study, including
a sensitivity analysis, to validate our approach. Other benchmarks and
real problems should be addressed in the future. These problems could
involve dealing with more than two objectives, so polar coordinates
should be used to visually understand the results
\cite{Li17read}. Also, other MOEA algorithms available in the
literature, such as SPEA or MOEA/D could also be compared.
